%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{assets/deedy-resume-openfont}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

\namesection{Anubhab} {Patnaik}\infoline{\href{mailto:anubhabr50@gmail.com}{ \underline{anubhabr50@gmail.com}} | Bhubaneswar, India}\\\vspace{4pt}\linksline{\descript{\href{https://github.com/fuzzymfx}{ \underline{GitHub} | }}\descript{\href{https://www.linkedin.com/in/anubhabpatnaik0530/}{ \underline{Linkedin} | }}\descript{\href{https://leetcode.com/anubhabr50/}{ \underline{LeetCode} | }}\descript{\href{http://anubhavp.dev}{ \underline{Portfolio} | }}\descript{\href{https://anubhavp.dev/blog}{ \underline{Blog} | }}\descript{\href{https://drive.google.com/drive/folders/1h-Anp3M7kSEChJMMS27pkqr4ZByXmnEU?usp=sharing}{ \underline{Certificates}}}}\underlineheader{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

\runsubsection{\href{http://www.silicon.ac.in}{ \underline{Silicon Institute of Technology, Bhubaneswar}}}\hspace*{\fill}  \location{July 2019 - May 2023}\\
\descript{B. Tech Computer Science and Engineering}\hspace*{\fill}\location{Bhubaneswar, India}\\
GPA: 8.84\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %
  %     Experience
  %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{Work Experience}
  \runsubsection{\href{http://squibix.com/}{ \underline{Squbix Digital}}}\descript{| Fullstack blockchain developer}\hfill \location{Bhubaneswar | July 3rd, 2022 – Jan 3rd, 2023}
      \begin{tightemize}
       \item Designed and developed the {\href{https://squbix.com/}{ \underline{Squbix Website}}}. Refactored React-Native applications with better UI and implemented offline storage, push notifications, and built an internal ERP system to monitor the attendance and tasks of employees.
       \item Built backend APIs using NodeJs. Configured optional parameters to switch between different blockchains. Refactored the JS-based SDK to TypeScript and NodeJs. Used mocha for unit testing.
       \item Modified the existing DID pallet using rust and substrate to store identity information in the blockchain with additional unit tests. Collaborated on the wallet transfer PWA to cater to the need of existing users of the older blockchain.
      \end{tightemize}
      \sectionsep
  \runsubsection{\href{https://www.afixi.com/}{ \underline{Afixi Technologies Pvt. LTD}}}\descript{| Freelance }\hfill \location{Bhubaneswar | March 2022 – April 2022}
      \begin{tightemize}
    \item Set up a platform to handle 30\% of DDEX submissions using AWS S3 \& Go, and automated uploading of music on YouTube.
\end{tightemize}
      \sectionsep
  \runsubsection{\href{http://ebibil.com/}{ \underline{E-Bibil Technologies}}}\descript{| Front-end developer}\hfill \location{WFH | July 27th, 2021 – Sep 27th, 2021}
      \begin{tightemize}
    \item Collaborated on the Django web app to integrate with ML models for a smart parking system to identify \& recognize the license plate using python and OpenCV for the ANPR system with a 67\% accuracy.
    \item Implemented a PWA using react \& django for the admin panel that manages 40\% of the workload in the parking system.
\end{tightemize}
      \sectionsep
      \runsubsection{\href{https://www.linkedin.com/company/brainlox/}{ \underline{Brainlox Technologies}}}\descript{| Python Tutor}\hfill \location{WFH | July 16th, 2021 – Oct 9th, 2021}
      \begin{tightemize}
    \item Tutored students on the basics of computer Science \& programming using Python.
    \end{tightemize}
      \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technologies worked with}
\raggedright
\begin{tabular}{ l l }
\descript{Programming Languages} & {\location{\textbf{C/C++}, \textbf{Python}, JavaScript/TypeScript, PHP, Rust, SQL}} \\
\descript{Libraries/ Frameworks} & {\location{Numpy, Pandas, Sk-Learn, React, ReactNative, NodeJs, Django, Flutter, Substrate}} \\
\descript{Developer Tools \& Platforms} & {\location{Git, gh-actions, Docker, AWS, Firebase, MongoDB}} \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Projects
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects \& Hacks}
\raggedright

\runsubsection{\large{QTree}}
\descript{{| \href{https://github.com/fuzzymfx/qd-compression}{ \underline{Source-QTree}}} {| \href{https://anubhavp.dev/blog/qtree.html}{ \underline{Live}}}} \hfill \location{JavaScript, Canvas, HTML, }\\
Inspired by {\href{https://github.com/vogievetsky/KoalasToTheMax}{ \underline{KoalasToTheMax}}}, QTree is a short live demonstration of image compression and decompression using Quadtrees, that partitions a two-dimensional image by recursively subdividing it into four quadrants. \\
\sectionsep

\runsubsection{\large{W3BCHAT \& Rokio}}
\descript{{| \href{https://github.com/fuzzymfx/w3bchat-dapp}{ \underline{Source-W}}} {| \href{https://bit.ly/sdchapp}{ \underline{Live}}}{| \href{https://github.com/fuzzymfx/rust-tokio-chat-server}{ \underline{T}}}} \hfill \location{GunJS, Svelte, Rust, Tokio, Substrate, React, Firebase, gh-actions}\\
W3BCHAT is a decentralized multi-client chat app that uses a graph-db built to mimic the demonstration of a blockchain. Rokio is a blogging platform written in rust for super fast performance and excellent memory management.\\
\sectionsep

\runsubsection{\large{Bee \& Plix}}   
\descript{| \href{https://github.com/fuzzymfx/Movie-recommendation}{ \underline{Source-MR}}{| \href{https://github.com/fuzzymfx/b}{ \underline{Source-B}}}{| \href{https://github.com/fuzzymfx/Movie-rating-prediction}{ \underline{Source- RP}}}}\hfill \location{Rust, Pandas, Sklearn, NLP, LP, BitTorrent}\\
A self-made custom BitTorrent client to download files \& movies with an item-based collaborative movie recommendation system based on user ratings and the number of ratings and a rating prediction system to classify movie reviews as good/bad.\\
\sectionsep


\runsubsection{\large{ZUZU \& BLOG-2}}
\descript{| \href{https://github.com/fuzzymfx/blogapp}{ \underline{S-Old}}| \href{https://github.com/fuzzymfx/zuzu}{ \underline{Source}}| \href{https://anubhavp.dev/zuzu}{ \underline{Live}}}
\hfill \location{Node, Django REST, Bootstrap, React Hooks, SQLite3, AWS EC2, gh-actions}\\
A static site generator with rss, pdf generators with search feat., \& custom themes. BLOG II is a multi-client blog with token-based auth. \\
\sectionsep


\runsubsection{\large{RESOC}}
\descript{| \href{https://github.com/fuzzymfx/resoc}{ \underline{Source-Resoc}}{| \href{https://auth-notesapp-test.web.app/}{ \underline{Live}}}}\hfill \location{React, React-Native, React-Bootstrap, Firebase, Cloud Firestore}\\
A website for accessing free academic resources with a markdown reader, assignments, a task manager, and a chat section.\\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Awards
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Honors \& Awards}
\begin{tightemize}  
\item Semi-Finalist: Binance' 2022, \href{https://nirmansilicon.tech/}{\underline{Nirman' 2022}} \& ED Cell -Ideathon 2022 \\
\item Best Delegate: XIMUN' 23 LHSMUN '20. High Commendation-I SITMUN(2020 \& 2021). Special mention: Carmel Summit '15. \\
\end{tightemize}
% \sectionsep
\section{Volunteer Experience}
\begin{tightemize} 
\item Co-founder - \underline{\href{https://cbrtl.github.io}{cbrtl}}: A FOSS platform for programmers who like to craft fun projects together. \textbf{2022}\\
\item Co-founder \& Joint Secretary, Silicon Wing of Technical and Coding Hub, the first official coding club of the College. \textbf{2021}.\\
\item Chairperson - \textbf{2022-23} of the prestigious IEEE Students’ Chapter, Silicon Institute of Technology.\\
\end{tightemize}
\ 
\end{document}